### 2011-12-01 plos_template.tex

Although companies like 23andMe are willing to contribute to science it is not easy for individual scientists to get hold of the data. This arises mainly due to privacy concerns of the customers. A possible solution to this can be a crowdsourcing platform that aggregates genetical and phenotypical information of people who are willing to share their data with the general public and have given their informed consent. In our study we investigated if there would be interest in such a crowd sourcing platform, how many people would be willing to share their genetic and phenotypic information with the public and built such a platform.

>>>>

Although companies like 23andMe are willing to contribute to science it is not easy for individual scientists to get hold of the data. This arises mainly due to privacy concerns of the customers. Nevertheless there are individual customers who are willingly sharing their data. Most do though by uploading it to their personal website or to software repositories like GitHub. While this is makes it possible to use the data, it requires a lot of work to keep track of all new genotyping data that is available to the public. While projects like the SNPedia try to keep track of all the files, this still does not allow to perform GWAS, as the phenotypic information is not attached to the genetic information. Projects that attach the phenotype to the genetic information, like the Personal Genome Project, still don't allow for an easy re-use of the data.

A possible solution to this can be a community-driven platform that aggregates genetical and phenotypical information of people who are willing to share their data with the general public and have given their informed consent. In our study we investigated if there would be interest in such a crowd sourcing platform, how many people would be willing to share their genetic and phenotypic information with the public and built such a platform.
